---
title: "Untitled"
author: "Felix"
date: "2/2/2026"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
pacman::p_load(
  MASS,
  dplyr,
  tibble,
  purrr,
  readr,
  ggplot2,
  tidyr,
  broom,
  lubridate,
  here,
  scales
)

dt <- lubridate::today()
dir.create("results", showWarnings = FALSE)
dir.create("figures", showWarnings = FALSE)

```


#0) ONE SOURCE OF TRUTH: DGP COEFFICIENTS

```{r}
COEF <- list(
  p1 = list(b0 = 0.0, post = 0.2, tx = -0.2, int = 0.0,
            female = 1.2, hisp = -0.8, zpcs = -0.2),
  p2 = list(b0 = 7.0, post = 0.2, tx =  0.2, int = 0.0,
            female = 0.4, hisp = -0.2, zpcs = -0.4)
)

# --- helper: log-uniform draw for extremes ---
rlogunif <- function(n, min_val, max_val) {
  if (n <= 0) return(numeric(0))
  exp(runif(n, log(min_val), log(max_val)))
}

# --- helper: extreme value ranges ---
extreme_range <- function(mag_level) {
  switch(as.character(mag_level),
         "1" = c(5e4, 1e6),
         "2" = c(5e4, 2e6),
         "3" = c(5e4, 3e6),
         stop("Invalid magnitude_level"))
}

```

#1) DGP: two-part Gamma with extremes

```{r}
simulate_panel_data <- function(
  n, magnitude_level, prop_extreme = 0.01,
  p_treated = 0.5, sigma_u = 0.5, rho = 0.5,
  gamma_shape = 3,
  COEF
) {
  T <- 2; N <- n * T
  ids <- rep(1:n, each = T)
  ind_post <- rep(0:1, times = n)

  # covariates
  ind_tx_i     <- rbinom(n, 1, p_treated)
  ind_female_i <- rbinom(n, 1, 0.5)
  HISPANX_i    <- rbinom(n, 1, 0.2)
  #INSCOV_i     <- sample(1:3, n, replace = TRUE)

  ind_tx     <- rep(ind_tx_i, each = T)
  ind_female <- rep(ind_female_i, each = T)
  HISPANX    <- rep(HISPANX_i, each = T)
  #INSCOV     <- factor(rep(INSCOV_i, each = T))

  # PCS42 with correlation (keep your approach)
  Sigma <- matrix(c(1, rho, rho, 1), 2, 2)
  pcs   <- MASS::mvrnorm(n, mu = c(50, 50), Sigma = Sigma)
  PCS42 <- as.vector(t(pcs))
  zPCS  <- (PCS42 - 50) / 10  # standardized PCS42

  # random intercept (kept for fidelity; not used in lp by design)
  u_i <- rnorm(n, 0, sigma_u)
  u   <- u_i[ids]

  # Part 1: logistic >0 (use COEF)
  lp_cov <- COEF$p1$b0 +
    COEF$p1$post   * ind_post +
    COEF$p1$tx     * ind_tx +
    COEF$p1$int    * (ind_post * ind_tx) +
    COEF$p1$female * ind_female +
    COEF$p1$hisp   * HISPANX +
    COEF$p1$zpcs   * zPCS

  pr_pos  <- plogis(lp_cov)
  ind_gt0 <- rbinom(N, 1, pr_pos)

  # Part 2: Gamma for positives (use COEF)
  lp_cont <- COEF$p2$b0 +
    COEF$p2$post   * ind_post +
    COEF$p2$tx     * ind_tx +
    COEF$p2$int    * (ind_post * ind_tx) +
    COEF$p2$female * ind_female +
    COEF$p2$hisp   * HISPANX +
    COEF$p2$zpcs   * zPCS

  mu <- exp(lp_cont)
  shape <- gamma_shape
  scale <- mu / shape

  TOTEXPYY <- rep(0, N)
  TOTEXPYY[ind_gt0 == 1] <- rgamma(sum(ind_gt0),
                                   shape = shape,
                                   scale = scale[ind_gt0 == 1])

  # inject extremes
  K_ext <- rbinom(1, N, prop_extreme)
  if (K_ext > 0) {
    rng <- extreme_range(magnitude_level)
    idx_ext <- sample.int(N, size = K_ext, replace = FALSE)
    TOTEXPYY[idx_ext] <- rlogunif(K_ext, rng[1], rng[2])
  } else idx_ext <- integer(0)

  tibble(
    DUPERSID = factor(ids),
    ind_post, ind_tx, ind_female, HISPANX, PCS42, zPCS, #INSCOV,
    ind_gt0 = ind_gt0,
    TOTEXPYY = TOTEXPYY,
    extreme_flag = as.integer(seq_len(N) %in% idx_ext),
    magnitude_level, prop_extreme
  )
}

```


#2) Treatments for extreme values (UPDATED)
# - mean/median preserved uses values > q95 only
# - truncation removes rows (not NA)

```{r}
treat_extremes_df <- function(dat, method = "raw") {
  if (method == "raw") return(dat)

  q95 <- quantile(dat$TOTEXPYY, 0.95, na.rm = TRUE)

  if (method == "topcode") {
    dat$TOTEXPYY <- pmin(dat$TOTEXPYY, q95)
    return(dat)
  }

  if (method == "mean_adj") {
    m <- mean(dat$TOTEXPYY[dat$TOTEXPYY > q95], na.rm = TRUE)
    dat$TOTEXPYY[dat$TOTEXPYY > q95] <- m
    return(dat)
  }

  if (method == "median_adj") {
    m <- median(dat$TOTEXPYY[dat$TOTEXPYY > q95], na.rm = TRUE)
    dat$TOTEXPYY[dat$TOTEXPYY > q95] <- m
    return(dat)
  }

  if (method == "truncate") {
    dat <- dat %>% filter(TOTEXPYY <= q95)
    return(dat)
  }

  stop("Unknown treatment method")
}

```

#3) Safe Gamma fit wrapper

```{r}
safe_gamma_fit <- function(dat) {
  dat2 <- dat %>% filter(ind_gt0 == 1, is.finite(TOTEXPYY), TOTEXPYY > 0)
  if (nrow(dat2) < 10) return(NULL)

  out <- tryCatch({
    glm(
      TOTEXPYY ~ ind_post*ind_tx + ind_female + HISPANX + zPCS,
      data = dat2,
      family = Gamma(link = "log"),
      control = glm.control(maxit = 100, epsilon = 1e-8)
    )
  }, error = function(e) NULL)

  out
}

```

#3b) Effect size helper:
```{r}
compute_sd_ref <- function(dat, ref = c("control_pre", "pooled_pre", "control_all")) {

  if (missing(dat) || is.null(dat)) {
    stop("compute_sd_ref(): you must pass a data.frame/tibble as 'dat' (e.g., compute_sd_ref(dat, ref='control_pre')).")
  }

  ref <- match.arg(ref)

  dref <- switch(
    ref,
    control_pre = dat %>% dplyr::filter(ind_tx == 0, ind_post == 0),
    pooled_pre  = dat %>% dplyr::filter(ind_post == 0),
    control_all = dat %>% dplyr::filter(ind_tx == 0)
  )

  sd_ref <- sd(dref$TOTEXPYY, na.rm = TRUE)

  # guard against degenerate / invalid SD
  if (!is.finite(sd_ref) || sd_ref <= 0) return(NA_real_)
  sd_ref
}

```

#4) ATT computation (RQ4): Estimated + TRUE using same COEF
```{r}
compute_ATT_hat <- function(dat, fit_logit, fit_gamma) {

  treated_post <- dat %>% filter(ind_tx == 1, ind_post == 1)
  if (nrow(treated_post) == 0) return(NA_real_)

  treated_cf <- treated_post %>% mutate(ind_tx = 0)

  # Part 1: Pr(Y>0)
  p_obs <- predict(fit_logit, newdata = treated_post, type = "response")
  p_cf  <- predict(fit_logit, newdata = treated_cf,   type = "response")

  # Part 2: E[Y|Y>0] (Gamma log link; response is on original scale)
  mu_obs <- predict(fit_gamma, newdata = treated_post, type = "response")
  mu_cf  <- predict(fit_gamma, newdata = treated_cf,   type = "response")

  mean(p_obs * mu_obs - p_cf * mu_cf)
}

compute_true_ATT <- function(dat, COEF) {

  treated_post <- dat %>% filter(ind_tx == 1, ind_post == 1)
  if (nrow(treated_post) == 0) return(NA_real_)

  treated_cf <- treated_post %>% mutate(ind_tx = 0)

  # TRUE Part 1
  lp1_obs <- COEF$p1$b0 +
    COEF$p1$post   * treated_post$ind_post +
    COEF$p1$tx     * treated_post$ind_tx +
    COEF$p1$int    * (treated_post$ind_post * treated_post$ind_tx) +
    COEF$p1$female * treated_post$ind_female +
    COEF$p1$hisp   * treated_post$HISPANX +
    COEF$p1$zpcs   * treated_post$zPCS
  p_obs <- plogis(lp1_obs)

  lp1_cf <- COEF$p1$b0 +
    COEF$p1$post   * treated_cf$ind_post +
    COEF$p1$tx     * treated_cf$ind_tx +
    COEF$p1$int    * (treated_cf$ind_post * treated_cf$ind_tx) +
    COEF$p1$female * treated_cf$ind_female +
    COEF$p1$hisp   * treated_cf$HISPANX +
    COEF$p1$zpcs   * treated_cf$zPCS
  p_cf <- plogis(lp1_cf)

  # TRUE Part 2
  lp2_obs <- COEF$p2$b0 +
    COEF$p2$post   * treated_post$ind_post +
    COEF$p2$tx     * treated_post$ind_tx +
    COEF$p2$int    * (treated_post$ind_post * treated_post$ind_tx) +
    COEF$p2$female * treated_post$ind_female +
    COEF$p2$hisp   * treated_post$HISPANX +
    COEF$p2$zpcs   * treated_post$zPCS
  mu_obs <- exp(lp2_obs)

  lp2_cf <- COEF$p2$b0 +
    COEF$p2$post   * treated_cf$ind_post +
    COEF$p2$tx     * treated_cf$ind_tx +
    COEF$p2$int    * (treated_cf$ind_post * treated_cf$ind_tx) +
    COEF$p2$female * treated_cf$ind_female +
    COEF$p2$hisp   * treated_cf$HISPANX +
    COEF$p2$zpcs   * treated_cf$zPCS
  mu_cf <- exp(lp2_cf)

  mean(p_obs * mu_obs - p_cf * mu_cf)
}

```


#5) One replication under one scenario (UPDATED)
- uses zPCS in models
- returns interaction estimates + ATT outputs
- adds ATT effect size (d_est, d_true, d_bias) using baseline SD

```{r}
run_one <- function(n, magnitude_level, prop_extreme, gamma_shape, treatment, COEF,
                    es_ref = "control_pre") {

  dat <- simulate_panel_data(
    n = n,
    magnitude_level = magnitude_level,
    prop_extreme = prop_extreme,
    gamma_shape = gamma_shape,
    COEF = COEF
  )

  # Apply treatment at the DATAFRAME level
  dat <- treat_extremes_df(dat, treatment)

  # Logistic
  fit1 <- glm(ind_gt0 ~ ind_post*ind_tx + ind_female + HISPANX + zPCS,
              data = dat, family = binomial)
  c1 <- coef(summary(fit1))["ind_post:ind_tx", c("Estimate","Std. Error")]

  # Gamma fit object (safe)
  fit2 <- safe_gamma_fit(dat)
  if (is.null(fit2)) {
    c2 <- c(NA_real_, NA_real_)
  } else {
    c2 <- coef(summary(fit2))["ind_post:ind_tx", c("Estimate","Std. Error")]
  }

  # ATT requires gamma object
  ATT_hat  <- if (!is.null(fit2)) compute_ATT_hat(dat, fit1, fit2) else NA_real_
  ATT_true <- compute_true_ATT(dat, COEF)
  ATT_bias <- ATT_hat - ATT_true

  # --- Effect size (Cohen's d style): standardize ATT by baseline SD ---
  sd_ref <- compute_sd_ref(dat, ref = es_ref)
  d_hat  <- ifelse(is.na(ATT_hat)  || is.na(sd_ref), NA_real_, ATT_hat  / sd_ref)
  d_true <- ifelse(is.na(ATT_true) || is.na(sd_ref), NA_real_, ATT_true / sd_ref)
  d_bias <- d_hat - d_true

  tibble(
    model = c("logit", "gamma", "ATT"),
    est   = c(unname(c1[1]), unname(c2[1]), ATT_hat),
    se    = c(unname(c1[2]), unname(c2[2]), NA_real_),
    true  = c(COEF$p1$int, COEF$p2$int, ATT_true),
    bias  = c(unname(c1[1]) - COEF$p1$int,
              unname(c2[1]) - COEF$p2$int,
              ATT_bias),

    # effect-size columns (only meaningful for ATT row; NA for others)
    d_est  = c(NA_real_, NA_real_, d_hat),
    d_true = c(NA_real_, NA_real_, d_true),
    d_bias = c(NA_real_, NA_real_, d_bias),

    n = n, prop_extreme, magnitude_level, gamma_shape, treatment
  )
}

run_mc <- function(B, n, magnitude_level, prop_extreme, gamma_shape, treatment, COEF,
                   es_ref = "control_pre") {
  results <- replicate(
    B,
    run_one(n, magnitude_level, prop_extreme, gamma_shape, treatment, COEF, es_ref = es_ref),
    simplify = FALSE
  )
  bind_rows(results)
}

```

#Step 1: Representative dataset (histograms + model fits)
```{r}
set.seed(123)
dat_example <- simulate_panel_data(
  n = 1000,
  magnitude_level = 1,
  prop_extreme = 0.05,
  gamma_shape = 3,
  COEF = COEF
)

p1 <- ggplot(dat_example, aes(x = TOTEXPYY)) +
  geom_histogram(bins = 100, fill = "skyblue", color = "black") +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "Histogram of TOTEXPYY", x = "Spending", y = "Count") +
  theme_minimal()

p2 <- ggplot(dat_example, aes(x = TOTEXPYY)) +
  geom_histogram(bins = 100, fill = "seagreen", color = "black") +
  scale_x_log10(labels = scales::comma) +
  labs(title = "Histogram of TOTEXPYY (log scale)", x = "Spending (log)", y = "Count") +
  theme_minimal()

print(p1); print(p2)

fit_logit <- glm(ind_gt0 ~ ind_post*ind_tx + ind_female + HISPANX + zPCS,
                 data = dat_example, family = binomial)

fit_gamma <- glm(TOTEXPYY ~ ind_post*ind_tx + ind_female + HISPANX + zPCS,
                 data = dat_example %>% filter(ind_gt0 == 1),
                 family = Gamma(link = "log"))

summary(fit_logit)
summary(fit_gamma)

```

#Step 2: Full Monte Carlo across scenarios
```{r}
n_vals <- c(5000, 10000, 20000)
prop_extreme_vals <- c(0.01, 0.05, 0.10)
magnitude_vals <- c(1, 2, 3)
treatment_methods <- c("raw", "topcode", "mean_adj", "median_adj", "truncate")

grid <- expand.grid(
  n = n_vals,
  prop_extreme = prop_extreme_vals,
  magnitude_level = magnitude_vals,
  treatment = treatment_methods,
  stringsAsFactors = FALSE
)

set.seed(2025)
B <- 500

# Effect size reference group choice:
# "control_pre" (recommended), "pooled_pre", or "control_all"
ES_REF <- "control_pre"

all_df <- pmap_dfr(
  grid,
  ~ run_mc(B, ..1, ..3, ..2, gamma_shape = 3, ..4, COEF = COEF, es_ref = ES_REF)
)

# Save raw simulation output
saveRDS(all_df, file = here::here(paste0("results/all_df_", dt, ".RDS")))
write.csv(all_df, file = here::here(paste0("results/all_df_", dt, ".csv")), row.names = FALSE)

```


#Summarise results (includes ATT effect size columns)
```{r}
summ_grid <- all_df %>%
  group_by(model, n, prop_extreme, magnitude_level, treatment) %>%
  summarise(
    mean_est  = round(mean(est, na.rm = TRUE), 6),
    mean_true = round(mean(true, na.rm = TRUE), 6),
    bias      = round(mean(bias, na.rm = TRUE), 6),

    emp_se = round(sd(est, na.rm = TRUE), 6),
    rmse   = round(sqrt(mean((est - true)^2, na.rm = TRUE)), 6),

    coverage = round(
      mean((est - 1.96*se <= true) & (true <= est + 1.96*se), na.rm = TRUE),
      6
    ),

    # Effect size summary (ATT rows only; NA otherwise)
    d_mean   = round(mean(d_est, na.rm = TRUE), 6),
    d_emp_se = round(sd(d_est, na.rm = TRUE), 6),
    d_bias   = round(mean(d_bias, na.rm = TRUE), 6),

    n_fail = sum(is.na(est)),
    .groups = "drop"
  )

print(summ_grid)

saveRDS(summ_grid, file = here::here(paste0("results/summ_grid_", dt, ".RDS")))
write.csv(summ_grid, file = here::here(paste0("results/summ_grid_", dt, ".csv")), row.names = FALSE)

```


##4 FULL-FACTORIAL ANOVA (RQ answers)
```{r}
# ---- Gamma (Part 2 interaction): bias, SE, coverage ----
all_df_gamma <- all_df %>%
  dplyr::filter(model == "gamma") %>%
  dplyr::mutate(
    n = factor(n),
    prop_extreme = factor(prop_extreme),
    magnitude_level = factor(magnitude_level),
    treatment = factor(treatment),
    cover_ind = ifelse(is.na(est) | is.na(se), NA_real_,
                       as.numeric((est - 1.96*se <= true) & (true <= est + 1.96*se)))
  )

saveRDS(all_df_gamma, file = here::here(paste0("results/all_df_gamma_", dt, ".RDS")))
write.csv(all_df_gamma, file = here::here(paste0("results/all_df_gamma_", dt, ".csv")), row.names = FALSE)

# A) factorial ANOVA on gamma bias (rep-level)
aov_gamma_bias <- aov(bias ~ treatment * n * prop_extreme * magnitude_level, data = all_df_gamma)
summary(aov_gamma_bias)

# B) factorial ANOVA on gamma SE (rep-level)  <-- model SE
# aov_gamma_se <- aov(se ~ treatment * n * prop_extreme * magnitude_level, data = all_df_gamma)
# summary(aov_gamma_se)

# B v2) factorial ANOVA on gamma emp SE  (vs model SE, bc emp SE is the SD of the 500 est's of the coefficient, not the average of the model SE's, right?)
summ_grid_gamma <- summ_grid |> filter(model=="gamma")
aov_gamma_emp_se <- aov(
	emp_se ~ treatment * n * prop_extreme * magnitude_level, data = summ_grid_gamma )
summary(aov_gamma_emp_se) 

# C) coverage: scenario-level proportion (recommended)
cov_grid <- all_df_gamma %>%
  group_by(treatment, n, prop_extreme, magnitude_level) %>%
  summarise(coverage = mean(cover_ind, na.rm = TRUE), .groups = "drop")

aov_gamma_cov <- aov(coverage ~ treatment * n * prop_extreme * magnitude_level, data = cov_grid)
summary(aov_gamma_cov)

# ---- ATT (RQ4): ATT_hat, ATT_bias, and effect size across treatments ----
all_df_att <- all_df %>%
  dplyr::filter(model == "ATT") %>%
  dplyr::mutate(
    n = factor(n),
    prop_extreme = factor(prop_extreme),
    magnitude_level = factor(magnitude_level),
    treatment = factor(treatment)
  )

# ATT_hat across conditions
aov_att_hat <- aov(est ~ treatment * n * prop_extreme * magnitude_level, data = all_df_att)
summary(aov_att_hat)

# ATT_bias across conditions (recommended DV)
aov_att_bias <- aov(bias ~ treatment * n * prop_extreme * magnitude_level, data = all_df_att)
summary(aov_att_bias)

# Effect size (d_est) across conditions (optional but usually helpful)
aov_att_d <- aov(d_est ~ treatment * n * prop_extreme * magnitude_level, data = all_df_att)
summary(aov_att_d)

# Save ANOVA-ready datasets
write.csv(all_df_gamma, file = here::here(paste0("results/all_df_gamma_", dt, ".csv")), row.names = FALSE)
write.csv(all_df_att,   file = here::here(paste0("results/all_df_att_", dt, ".csv")), row.names = FALSE)
write.csv(cov_grid,     file = here::here(paste0("results/cov_grid_", dt, ".csv")), row.names = FALSE)

```


#Publication-ready plots

```{r}
# ---- 1) Gamma bias by treatment (scenario-level mean bias) ----
gamma_grid <- all_df_gamma %>%
  group_by(treatment, n, prop_extreme, magnitude_level) %>%
  summarise(
    mean_bias = mean(bias, na.rm = TRUE),
    mean_se   = mean(se, na.rm = TRUE),
    coverage  = mean(cover_ind, na.rm = TRUE),
    .groups = "drop"
  )

p_gamma_bias <- ggplot(gamma_grid, aes(x = treatment, y = mean_bias)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  geom_line(aes(group = 1)) +
  facet_grid(prop_extreme ~ magnitude_level, labeller = label_both) +
  labs(
    title = "Gamma (Part 2) Interaction: Mean Bias by Treatment",
    subtitle = "Rows = proportion extreme; Cols = magnitude level",
    x = "Treatment method",
    y = "Mean bias (est - true)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print(p_gamma_bias)
ggsave(here::here(paste0("figures/gamma_bias_by_treatment_", dt, ".png")),
       p_gamma_bias, width = 10, height = 7, dpi = 300)

# ---- 2) Gamma SE by treatment ----
p_gamma_se <- ggplot(gamma_grid, aes(x = treatment, y = mean_se)) +
  geom_point() +
  geom_line(aes(group = 1)) +
  facet_grid(prop_extreme ~ magnitude_level, labeller = label_both) +
  labs(
    title = "Gamma (Part 2) Interaction: Mean Model SE by Treatment",
    subtitle = "Rows = proportion extreme; Cols = magnitude level",
    x = "Treatment method",
    y = "Mean SE"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print(p_gamma_se)
ggsave(here::here(paste0("figures/gamma_se_by_treatment_", dt, ".png")),
       p_gamma_se, width = 10, height = 7, dpi = 300)

# ---- 3) Gamma coverage by treatment ----
p_gamma_cov <- ggplot(gamma_grid, aes(x = treatment, y = coverage)) +
  geom_hline(yintercept = 0.95, linetype = "dashed") +
  geom_point() +
  geom_line(aes(group = 1)) +
  facet_grid(prop_extreme ~ magnitude_level, labeller = label_both) +
  labs(
    title = "Gamma (Part 2) Interaction: Coverage by Treatment",
    subtitle = "Dashed line = nominal 0.95; Rows = prop extreme; Cols = magnitude",
    x = "Treatment method",
    y = "Coverage"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print(p_gamma_cov)
ggsave(here::here(paste0("figures/gamma_coverage_by_treatment_", dt, ".png")),
       p_gamma_cov, width = 10, height = 7, dpi = 300)

# ---- 4) ATT_hat and effect size by treatment ----
att_grid <- all_df_att %>%
  group_by(treatment, n, prop_extreme, magnitude_level) %>%
  summarise(
    mean_ATT_hat  = mean(est, na.rm = TRUE),
    mean_ATT_bias = mean(bias, na.rm = TRUE),
    mean_d        = mean(d_est, na.rm = TRUE),
    .groups = "drop"
  )

p_att_hat <- ggplot(att_grid, aes(x = treatment, y = mean_ATT_hat)) +
  geom_point() +
  geom_line(aes(group = 1)) +
  facet_grid(prop_extreme ~ magnitude_level, labeller = label_both) +
  labs(
    title = "ATT_hat (RQ4): Mean Estimated ATT by Treatment",
    subtitle = "Rows = proportion extreme; Cols = magnitude level",
    x = "Treatment method",
    y = "Mean ATT_hat"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print(p_att_hat)
ggsave(here::here(paste0("figures/att_hat_by_treatment_", dt, ".png")),
       p_att_hat, width = 10, height = 7, dpi = 300)

p_att_bias <- ggplot(att_grid, aes(x = treatment, y = mean_ATT_bias)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  geom_line(aes(group = 1)) +
  facet_grid(prop_extreme ~ magnitude_level, labeller = label_both) +
  labs(
    title = "ATT_bias (RQ4): Mean ATT Bias by Treatment",
    subtitle = "Rows = proportion extreme; Cols = magnitude level",
    x = "Treatment method",
    y = "Mean ATT bias (ATT_hat - ATT_true)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print(p_att_bias)
ggsave(here::here(paste0("figures/att_bias_by_treatment_", dt, ".png")),
       p_att_bias, width = 10, height = 7, dpi = 300)

# ---- 6) Effect size (d) by treatment (optional but recommended) ----
p_att_d <- ggplot(att_grid, aes(x = treatment, y = mean_d)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  geom_line(aes(group = 1)) +
  facet_grid(prop_extreme ~ magnitude_level, labeller = label_both) +
  labs(
    title = "ATT Effect Size (d): Mean Standardized ATT by Treatment",
    subtitle = paste0("Standardized by baseline SD (", ES_REF, "); Rows = prop extreme; Cols = magnitude"),
    x = "Treatment method",
    y = "Mean d (ATT / baseline SD)"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

print(p_att_d)
ggsave(here::here(paste0("figures/att_effect_size_d_by_treatment_", dt, ".png")),
       p_att_d, width = 10, height = 7, dpi = 300)

# Export scenario-level grids for tables
write.csv(gamma_grid, file = here::here(paste0("results/gamma_grid_", dt, ".csv")), row.names = FALSE)
write.csv(att_grid,   file = here::here(paste0("results/att_grid_", dt, ".csv")), row.names = FALSE)

```






